### 2015-04-23 Paper_v1.tex
Still updating

Model calibration or parameter estimation follows the model construction step.  In this step the model is trained against experimental data to determine the model parameters that give a good fit. After model design and calibration, validation is done wherein the model output is validated against unseen experimental data. If validation leads to unsatisfactory results model design and calibration are performed once again. This process is done iteratively till successful results are obtained from validation step. \\

The objective function in Equation 5 is minimized using appropriate optimization technique to estimate the model parameters. These problems are generally multi-modal i.e. contain multiple local optima traditional. Hence we cannot use local optimization techniques cannot be used to solve these problems. In many of these problems derivative information is absent or the objective function may be discontinuous. This hinders the use of deterministic optimization techniques that require the problem to be convex and other derivative/gradient based optimization methods. Most of these methods are computationally expensive and for optimization of large-scale ODE systems, this becomes prohibitively expensive. Heuristic optimization techniques like genetic algorithm and differential evolution offer an attractive option in finding globally optimum solution or close to global optimum solution. However most of the population-based heuristics take a large number of function evaluations and have computationally complex operations, which reduces their effectiveness in finding feasible solutions with limited computational resources and time.

>>>>

Model calibration or parameter estimation follows the model construction step.  In this step the model is trained against experimental data to determine the model parameters that give a good fit against experimental data. Model simulation using these parameters is then done and the results are validated using hitherto unseen experimental data. If validation leads to unsatisfactory results model construction and calibration are repeated iteratively till we get satisfactory results.

With the capacity to construct or formulate very large biological models, more often than not, parameter estimation has become the bottleneck in large scale mathematical modeling of biological systems. The problem of parameter estimation if generally framed as a non-linear optimization problem.

\textit  {\Large Equation needs to be written and explained terms}

The objective function in Equation 1 is minimized using appropriate optimization technique to estimate the model parameters. These problems are generally multi-modal i.e. contain multiple local optima traditional. Hence we cannot use local optimization techniques cannot be used to solve these problems. In many of these problems derivative information is absent or the objective function may be discontinuous. This hinders the use of deterministic optimization techniques that require the problem to be convex and other derivative/gradient based optimization methods. Most of these methods are computationally expensive and for optimization of large-scale ODE systems, this becomes prohibitively expensive. Heuristic optimization techniques like genetic algorithm and differential evolution offer an attractive option in finding globally optimum solution or close to global optimum solution. However most of the population-based heuristics take a large number of function evaluations and have computationally complex operations, which reduces their effectiveness in finding feasible solutions with limited computational resources and time.
